---
title: "Chordoma scRNA-seq Figure Reproducibility Review"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: show
    self_contained: true
    theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  out.width = "100%"
)

repo_root <- normalizePath("..", mustWork = TRUE)
preview_root <- file.path(getwd(), "panel_previews")

script_table <- data.frame(
  figure = paste0("Figure", 1:5),
  script = file.path(
    repo_root,
    paste0("Figure", 1:5),
    paste0("Figure", 1:5, "_Nature_Panels.R")
  ),
  stringsAsFactors = FALSE
)

style_script <- file.path(repo_root, "_figure_style.R")

result_sections <- read.delim(
  file.path(repo_root, "manuscript_sections.tsv"),
  stringsAsFactors = FALSE
)
result_sections$display_heading <- paste(result_sections$result_section, result_sections$provisional_heading, sep = ": ")

read_source <- function(path) {
  paste(readLines(path, warn = FALSE), collapse = "\n")
}

emit_source_block <- function(path) {
  cat("```r\n")
  cat(read_source(path))
  cat("\n```\n")
}

panel_label <- function(path) {
  label <- tools::file_path_sans_ext(basename(path))
  label <- gsub("_", " ", label)
  label <- sub("^fig", "Fig. ", label)
  label
}

panel_files <- function(figure) {
  panel_dir <- file.path(preview_root, figure)
  if (!dir.exists(panel_dir)) {
    return(character())
  }
  sort(list.files(panel_dir, pattern = "\\.png$", full.names = TRUE))
}

render_panel_gallery <- function(figure) {
  files <- panel_files(figure)
  if (!length(files)) {
    cat("<p class='missing-panels'>No rendered panel previews were found for ", figure, ".</p>\n", sep = "")
    return(invisible(NULL))
  }

  cat("<div class='panel-grid'>\n")
  for (file in files) {
    cat("<figure class='panel-card'>\n")
    cat("<img src='", knitr::image_uri(file), "' alt='", panel_label(file), "' />\n", sep = "")
    cat("<figcaption>", panel_label(file), "</figcaption>\n", sep = "")
    cat("</figure>\n")
  }
  cat("</div>\n")
}
```

<style>
body {
  font-family: "Roboto Condensed", "Arial Narrow", Arial, sans-serif;
  color: #1b1b1b;
}
h1, h2, h3 {
  font-weight: 500;
  letter-spacing: 0;
}
pre, code {
  font-family: Menlo, Consolas, "Liberation Mono", monospace;
  font-size: 11px;
}
.main-container {
  max-width: 1320px !important;
}
.panel-grid {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(360px, 1fr));
  gap: 18px;
  margin: 18px 0 30px 0;
}
.panel-card {
  border: 1px solid #d9d9d9;
  border-radius: 4px;
  padding: 10px;
  margin: 0;
  background: #fff;
}
.panel-card img {
  display: block;
  width: 100%;
  height: auto;
}
.panel-card figcaption {
  margin-top: 8px;
  font-size: 12px;
  color: #4d4d4d;
}
.missing-panels {
  color: #9a3412;
  font-weight: 500;
}
table {
  font-size: 13px;
}
</style>

# Overview

This HTML review document combines the final Nature-style figure panels with the R code used to generate them. It is intended as a convenient manuscript-review artifact: reviewers can inspect the rendered panels and the exact plotting scripts in one downloadable file.

The large processed input objects are not embedded here. To regenerate the panels from data, place the required files listed in `data_manifest.tsv` into the repository and run:

```r
source("run_all_nature_figures.R")
```

To rebuild this HTML report after the panels have been generated, run:

```r
source("review/render_review_html.R")
```

# Manuscript Result Mapping

```{r result-table}
knitr::kable(
  result_sections[, c("figure", "display_heading")],
  col.names = c("Figure code", "Provisional Results section")
)
```

# Shared Plotting Style

The final figure scripts use a common style helper for palettes, font setup, PDF export, and Nature-style themes.

```{r shared-style-code, results='asis'}
emit_source_block(style_script)
```

# Figure 1

```{r figure1-section, results='asis'}
render_panel_gallery("Figure1")
```

```{r figure1-code, results='asis'}
emit_source_block(script_table$script[script_table$figure == "Figure1"])
```

# Figure 2

```{r figure2-section, results='asis'}
render_panel_gallery("Figure2")
```

```{r figure2-code, results='asis'}
emit_source_block(script_table$script[script_table$figure == "Figure2"])
```

# Figure 3

```{r figure3-section, results='asis'}
render_panel_gallery("Figure3")
```

```{r figure3-code, results='asis'}
emit_source_block(script_table$script[script_table$figure == "Figure3"])
```

# Figure 4

```{r figure4-section, results='asis'}
render_panel_gallery("Figure4")
```

```{r figure4-code, results='asis'}
emit_source_block(script_table$script[script_table$figure == "Figure4"])
```

# Figure 5

```{r figure5-section, results='asis'}
render_panel_gallery("Figure5")
```

```{r figure5-code, results='asis'}
emit_source_block(script_table$script[script_table$figure == "Figure5"])
```

# Session Information

```{r session-info}
sessionInfo()
```
